\section{Features}

\subsection{Selected Attributes}
\begin{description}
	\item[Priority]{Importance of a feature to the functionality of the overall product.  This is rated on a scale of Useful (nice to have), Important (needed for full functionality), and Critical (needed for basic functionality).}
	\item[Risk]{How likely it is that a feature will experience delays or undesired outcomes. Rated on a scale from low to high.}
	\item[Effort]{The relative time required to implement a given feature.  This is rated on a scale from low to high.}
	\item[Research]{Relative amount of research required to implement a given feature. Some features may be highly technical.}
	\item[Version]{The approximated release version which will contain the feature.}
	\item[Reason]{The need the feature is fufilling.}
\end{description}

\newcommand{\lw}{Low}
\newcommand{\md}{Medium}
\newcommand{\hh}{High}
\subsection{Feature Table}
\begin{tabularx}{\textwidth}{|X|c|c|c|c|c|X|}
	\hline
	\bf Feature &\bf Priority &\bf Risk &\bf Effort &\bf Research &\bf Version &\bf Reason \\ \hline
	Parse / analyze HTML header information & Critical & \lw & \md & \md & v1.0 & Source of basic webpage and server data. \\ \hline
	Examine server file tree & Critical & \md & \lw & \lw & v1.0 & Potentially sensitive information may be hosted publicly. \\ \hline
	Save crawl results to database & Critical & \md & \hh & \lw &v2.0 & Results must be saved for report generation and statistics tracking. \\ \hline
	Report crawl results & Critical & \hh & \md & \md &v1.0 & Results must be distributed to Alan so that he may report customized results to the user. \\ \hline
	Parse and analyze Javascript files & Critical & \lw & \hh & Very High &v3.0 & Javascript files are indicative of production framework. \\ \hline
	Parse / analyze HTML form information & Important & \lw & \hh & \hh &v1.5  & Forms may indicate which frameworks generated them. \\ \hline
	Examine site security certificates & Important & \md & \lw & \md &v2.0 & Check for expired certificates. \\ \hline
	Maintain operations tracelog & Important & \hh & \lw & \lw &v1.0 & Allows for traceback of operations for quality assurance and testing. \\ \hline
	Basic Web GUI & Useful & \lw & \lw & \lw &v3.0 & Allows a user to enter information from clients web site. \\ \hline
	Compare previous crawl information & Useful & \lw & \hh & \md &v3.0 & Allows the user to changes/improvements to website. \\ \hline
	Save search engine optimization (SEO) data & Useful & \lw & \lw & \md & v3.0 & Retains information for statistics on websites. \\ \hline
	Statistical analysis of crawls & Useful & \md & \hh & \md &v3.0 & Statistical tracking would give the client useful information about websites such as trends. \\ \hline
\end{tabularx}
\newpage
