\section{Project Background}
\subsection{Client}
	403 Security\index{403 Security}, a subsidiary of WDD Inc., analyzes and remediates insecure website design for its clients.  403 Security will also design a site from the ground up, if that service is requested; however, it should be noted that 403 Security focuses on backend almost exclusively--if it is necessary to designa  front end as well, they will collaborate with a design firm to ensure a quality product. \\\\
403 Security has stated that we are to be treated as an independent contractor, and, as such, they will have a fairly hands-off approach to the development of the Security Crawler system.

\subsection{Current System}

	Currently, 403 Security uses a professional penetration testing suite called Acunetix\index{Acunetix} to sweep and tes tpotential clients' sites.  Acunetix contains a myriad of testing tools, including a crawler similar to Security Crawler.

\subsection{Needs}
\begin{description}
\item[Need: ]{A system that will scan a site without performing a penetration test}
\item[Reason: ]{Penetration tests are illegal without the consent of the site's webmaster}
\item[If Unfulfilled: ]{Whenever a test is requested, 403 Security must follow an extensive, time consuming process to verify that the person requesting the scan is in fact the webmaster.  This can unnerve and lose potential customers.}
\item[Who is Affected:]{403 Security, who must do the requisite check on the client requesting a scan.}
\item[Benefits:]{403 Security will no longer have to do the cumbersome background checks on potential clients, avoiding possibly scaring them off, and allowing them to automate the process of scanning sites for security flaws.}\\
\item[Need: ]{An automated system for performing basics scans}
\item[Reason: ]{Basic, non-penetration scans can be time consuming for the technician who performs them}\item[If Unfulfilled:	]{Much time is spent performing cursory scans that could be easily automated}\item[Who is Affected:	]{403 Security, employees who must do easy, rather dull work that could spend their time pursuing more productive projects.}
\item[Benefits:	]{403 Security has more time to spend on non-scan projects. }\\
\item[Need: ]{An automated way to gather information on potential clients and vulnerabilities that need remediation.}
\item[Reason:	]{As a company, 403 Security is looking to expand its client base.}
\item[If Unfulfilled:	]{403 Security's client base will continue to grow as it has, without the increase this system could bring.}
\item[Benefits: ]{403 Security\index{403 Security} will be able to expand its client base with minimial increased effort.  They will also be able to build a profile for clients based around their known vulnerabilites.}
\end{description}

\subsection{Product Overview}

Security Crawler will be a web-based, self-contained system that takes an email and a URL.  It will perform a cursory security scan on the URL, emailing the results to the provided URL.  It will also catalogue the URL's results by email, allowing 403 Security to contact potential clients for future services.

\subsection{Summary of Capabilities}
\begin{tabularx}{\textwidth}{|X|X|}
    \hline
    {\bf Customer Benefits} & {\bf Supporting Features} \\ \hline
    Find and report security flaws in websites & Crawl website, output human-readable report \\ \hline
    Collect user emails & Require email for crawl request \\ \hline
    Gather crawled website statistics & Store crawled site informatino to database \\ \hline 
\end{tabularx}

\subsection{Assumptions}
\begin{itemize}
    \item Hosting done in Microsoft environments
    \item 403 Security will host any supporting software, such as a database
    \item Sotware will be available to the general public for use without 403 Security's explicit permission
    \item Web-based service
    \item Software will be used as a marketing tool
\end{itemize}

\subsection{Dependencies}
\begin{itemize}
    \item .NET Framework compatability
    \item 403 Security's ability to host services
\end{itemize}

\subsection{Constraints}
\begin{itemize}
    \item The web crawler cannot perform any penetration tests because of legal ramifications
    \item The system will be hosted on a Microsoft server and must be Microsoft compatible
    \item 403 Security's website will be the gateway to the program and therefore the front-end must be web-based
    \item The development team is only available until May 2012.  The project is due then.
\end{itemize}

\subsection{Alternatives and Competition}
\begin{description}
\item[Acunetix and other professional penetration testing software packages]{ are built to specifically do heavy-duty and comprehensive scans and simulated attacks. We are not aware of any software packages capable of determining specific web application platforms or third-party packages associated with said platforms.}

\item[Security Consultants]{ provide services that far outclass what our tool can do, but they are very expensive to hire.}
\end{description}
