To make the calendar more user friendly, the reminders button could be changed by getting rid of the plus symbol and replacing it with text that says "Reminder". No extra space is needed as there is space available to the right of the "All Calendars" heading. Additionally, we would change the "import" button to say "Import" rather than the current icon it has right now. Changing both the reminder button and the import button in this manner makes all of the buttons on this screen more consistent, with all of them having text.

For the reminders screen, the "plus" button could be made darker so that it stands out more. The initial design of the button blends in with the color theme, but it would be more benifical to make it easier to see since it is hard to see on the iPhone. Also, users might think that this button is disabled since the button is grey, and it is conventional for graphical user interfaces to grey a button out to signify that the button is disabled.

For the weather screen, the dark rounded rectangle that contains the weather could look like it is popping out, like a button. Making the weather look like a button tells the user that the weather is able to be clicked on to get more details on weather. The same would be done to the stocks area, since that can be clicked on too. Other than this, we find that the weather screen to have good design.

On the main menu, even though a user clicked on the calendar instead of the reminders to make a reminder, we find that the main menu screen to be good as it is. The icons are descriptive of what they do, and the text underneath the buttons describe exactly what screen they bring you to. To help the user that clicked on the calendar instead of reminders, the plus button could be changed to a "reminders" button, as stated above.