\section{User/Stakeholder Descriptions}
\begin{description}
\item[Alan Wlasuk] is our client and is the co-owner of WDD Software.  Alan is extremely experienced technically; he was a Bell Labs Fellow and knows how to conduct his company’s security scans himself. He founded WDD software in 2007, but had extensive experience in the security world prior to WDD’s founding.  Mr. Wlasuk is our primary contact within 403 Security.  He will be testing and giving feedback on the system on his Windows system.  He will also have access to 403 Security’s multiple windows server environments and any related databases.

\item[403 Security’s Marketing Team] is responsible for attracting new clients to 403 Security and will be responsible for receiving, organizing, and interpreting marketing data gathered from users of our tool. This marketing team will also be publicizing our tool and is the main direct 403 Security-side stakeholder in our tool. The marketing team will be interfacing with our database in whatever environment they wish.  We are not required to interact with their systems.  

\item[403 Security’s Developers] are responsible for hosting and maintaining our software and integrating it into their existing website. They have a very strong technical background and are comfortable with all commonly-used programming languages. Once we hand the product to the developers, the will need to be able to easily maintain and modify the software.  They will be working in a Windows and Windows Server environment.  All of 403 Security’s (Windows) hardware and software is available to them.

\item[External Webmasters] will use our tool to generate security reports about their website.  The crawler isn’t designed for savvy developers; average webmasters should be able to use it. They will be working in extremely varied environments, but will only interface with our web interface for the crawler.

\item[403 Security’s Legal Department] is concerned with the legality of our software. They are not technically experienced, but they have great experience with web security laws regarding penetration scanning and testing. They will need good documentation about the capabilities of our software and the reports it generates. The legal department will define success as a non-invasive crawler that only reports publicly accessible information.  They will not deal directly with the crawler, but only the documentation.

\item[External Individuals Who Don’t Own A Targeted Website] can access reports on websites they don’t own. As a result, we must restrict information presented in our report to publicly accessible information. These stakeholders are not being targeted, but are important to keep in mind as existing, since they could potentially be extremely technically savvy black hat hackers.  They will interact with the crawler purely from the web interface

\item[The Development Team] will design and implement the web crawler and all of its additional functionality.  They will be responsible for ensuring the legality of the project, as well as its functionality and stability.  The development team will not be maintaining the crawler, nor will they be integrating it into 403 Security’s existing web servers.  The team will be using varied environments, including Windows, Linux, and Mac.

\end{description}

