403 Security, a subsidiary of WDD Inc., is a web security firm specializing in analysis and remediation of a clients' websites.  Their current method of generating clients requires a prospective client to first request a scan.  The client's ownership of the site to be scanned is then checked, and a lengthy penetration scan is then performed on the site.  To reduce the overhead of this method of client generation, our team has been commissioned to create the Security Crawler system, a system that determines as many security vulnerabilities of a site without performing actual penetration tests.\\\\
This document contains all top level analysis of the crawler's top level requirements, including the basis needs and a listing of project stakeholders, critical features, dependencies and constraints. \\\\
A more detailed analysis of the features has also been included.  All use cases have been included, as well as test cases for each use case and all alternate flows present.  Dataflow diagrams down to second level analysis of all components have been included to provide a basis for architectural design.\\\\
A basic UI for the project is included, as well as all non-functional requirements.\\\\
Because the UI for the Security Crawler system is so basic, a proper usability test could not be conducted.  In lieu of a test for the Security Crawler system, a usability test for iOS 5 has been included in this document.  It documents testing for reminders, text messaging, weather, and calendar event functionality.
